Discrete Ordinates

### 2017-05-01 docprep/chapmeth.tex
Added a note about cone beams and deleted and old image from beamshapes

\subsection{Cone Source}
Pointy!

\subsection{Multi-cone Source}
All of the pointy!

>>>>

\subsection{Cone Source and Multi-cone Source}
Cone sources are identical to fan beam sources except for the rejection criteria used to determine whether or not a voxel is inside the beam. The rejection crieria is a function of only a single parameter, $\theta$, the maximum permissible angle between the center of the beam and a ray toward the point of interest.

The actual angle is $\zeta$ which is computed similarly to Eq.~\ref{eq:phicos} without the projection onto the $xy$ plane in Eq.~\ref{eq:zetacos} can be simplified to a simple summation since both $\vec{S}$ and $\vec{C}$ are unit vectors.

\begin{equation}\label{eq:zetacos}
\cos(\zeta) = \frac{<S_x, S_y, S_z>}{\sqrt{S_x^2 + S_y^2 + S_z^2}} \cdot \frac{<C_x, C_y, C_z>}{\sqrt{C_x^2 + C_y^2 + C_z^2}} = S_x C_x + S_y C_y + S_z C_z
\end{equation}

\begin{equation}\label{eq:zetacon}
|\zeta| < \theta
\end{equation}
